Knowledge Representation for Service Robots: A Survey

### 2014-04-17 krs-survey.tex
resolved conflict
added references and some text, to be adjusted and set in context...

%\documentclass[a4paper, twocolumn]{article}
\documentclass{IEEEtran}

\usepackage[utf8]{inputenc}

@@

\newcommand{\taxon}[2]{%
    \textbf{[#1] \emph{#2}}
}

@@

\section{Evaluation Criteria: A Typology of Knowledge Representation Requirements for Robotics}
\label{sect|features}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[utf8]{inputenc}

@@

\newcommand{\taxon}[2]{%
    \textbf{[#1] \emph{#2}}
}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}

@@

\todo{change wording, copied from other papers so far:}
\paragraph{Semantic maps}

Recent advances in object recognition however lead to more research on semantic
maps and thereby to a wider use of higher-level semantic knowledge in robotic
applications, though the ``level of semantics'' ranges from a  mere  classification
into different parts and object types~\cite{Rusu08RAS2} or the co-occurrence of
objects~\cite{vasudevan08} to environment representations in description
logic~\cite{zender2008conceptual}, statistical relational environment
models~\cite{limketkai05relational} and an embedding of spatial information
into an encyclopedic and common-sense knowledge base~\cite{tenorth10envmodel}.
The use of semantic maps as knowledge source for task planning has been
investigated by~\cite{galindo08taskplanning}. Other AI techniques that have
been used in robotics include the grounding of natural language in perception
and action \cite{Mavridis2006,kollar10natural}, planning of actions and
motions~\cite{wolfe10combined,kaelbling11planning}, and the generation of
robot controllers from logical constraints~\cite{kressgazit09planning}.

\paragraph{natural language understanding for direction following}
\cite{matuszek12commands}
\cite{duvallet13imitation}

\paragraph{(epsiodic) memories in robotics}

RACE \cite{rockel13ontology}
STRANDS?
CRAM$_m$ \cite{winkler13memory}

episodic memories in SOAR~\cite{nuxoll12episodic}

\paragraph{misc}
mining knowledge about object locations from the Web
\cite{zhou12webmining}

\todo{add something on the IEEE standard draft for a robotics and automation ontology}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\section{Evaluation Criteria: A Typology of Knowledge Representation Requirements for Robotics}
\label{sect|features}
